Open integrated distance sampling for modelling age-structured population dynamics

### 2024-09-01 Manuscript_Nilsen_Nater.qmd
Updated figures (manuscript repo & OSF)

![Detection parameters estimated from 10 distinct sets of simulated data (= colors). Upper panel depicts model parameters, and lower panels show derived estimated of effective strip width and mean detection probability. Dots represents true values (black for global values, colored for dataset-specific values), and density plot represent the posterior distributions for each model run.](Figures/SimCheck_Detects_Temps.png){#fig-sim-detection}

![Demographic rate parameters estimated from 10 distinct sets of simulated data (= colors). Upper panel show annual and seasonal survival probabilities, hyperparameters for the random effects model for recruitment (mean and sd), and lower panel show annual estimates of the recruitment rate. Dots represent true values (black for global values, colored for dataset-specific values), and density curves represent the posterior distributions from each model run.](Figures/SimCheck_VRs_Temps.png){#fig-sim-demo}

>>>>

![Vital rate and detection parameter averages estimated from 10 distinct sets of simulated data (= colors) using three model fits each. First row depicts posterior densities from each model run relative to the true value used to simulate data (black dashed line). Second and third rows visualize the distributions of Bayesian p-values (proportion of samples \> true value) and root-mean square deviations (RMSD) for all model runs, respectively. Purple lines and numbers mark the mean values across all model runs; dashed black line (second row only) marks the ideal Bayesian p-value of 0.5.](Figures/SimCheckMetrics_singleParams_Temps.png){#fig-sim-detection}

![Annual population density ($D_t$), detection probability ($p_t$), and recruitment rate ($R_t$) estimated from 10 distinct sets of simulated data (= colors) using three model fits each. First row depicts the relationship between posterior medians from each model run and the true value used to simulate data (purple solid line = relationship estimated from linear model with a = intercept and b = slope; black dashed line = perfect correlation). Second and third rows visualize the distributions of Bayesian p-values (proportion of samples \> true value) and root-mean square deviations (RMSD) for all model runs, respectively. Purple lines and numbers mark the mean values across all model runs; dashed black line (second row only) marks the ideal Bayesian p-value of 0.5. And equivalent figure showing posterior samples instead of posterior means is available in the supplementary material on OSF.](Figures/SimCheckMetrics_annualParams_median_Temps.png){#fig-sim-demo}
